Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-04-17 draft_report.qmd
Updated methodology relating to NACR data

This data was supplied by NACR. The data wasn’t available by GP Practice, so an alternative method was followed. Practices were allocated to a cluster and data was then supplied aggregated into clusters. In some cases, the data had to be redacted due to small numbers in the category. For the purposes of this analysis the redacted data item was reassigned an average value. The data used relates to the 2021 & 2022 calendar years, which are the most recent complete years, and following changes in the way rehabilitation has been delivered due to the Covid pandemic, most closely reflects the rehabilitation model now in place.

>>>>

This data was supplied by NACR from an extract taken in March 2024. The data wasn’t available by GP Practice, so an alternative method was followed. NACR was supplied with a list of practices, ICBs and the cluster to which they had been allocated by the Strategy Unit (SU). The data was then supplied to the SU aggregated into clusters and ICBs. The data relates to patients who started rehabilitation in 2021 or 2022 calendar years and were ACS or HF according to the NHS England reporting. These two years are the most recent complete years, and following changes in the way rehabilitation has been delivered due to the Covid pandemic, most closely reflect the rehabilitation model now in place. Patients needed to have GP Practice code recorded to be matched to a cluster. Those that didn't equated to 42637 patients that had either NO GP CODE completed, no matching GP Code or GMC Number added, representing 48% of patient records. Within the data included in this analysis, there are 11 clusters across 9 ICBs that have no rehabilitation data despite there being practices in the cluster. Due to these high levels of missing data the two cardiac rehabilitation metrics have been included in the presentations of the index of disparity and activity rates at a national level, but excluded from the regional and ICB level presentations.
